\bf Title

### 2024-01-18 article/paper_padic_spec.tex
def pol

We recall that that the smallest affine space of $K^n$ containing a set $S \subset K^n$ is called its
\emph{affine hull} and denoted $\aff{S}$.
The assumption on forms $\ell_i$ in \Cref{def_polyhedra} implies that the constraint
$\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ defines exactly the affine hull of $P$, in other words
$\aff{P} = \{x \in K^n : m_j(x) = 0,
j=1,\ldots,e\}$. The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$,
$\aff{P}=K^n$ and $P$ has dimension $n$).
The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d)
< +\infty\}$.
Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.

@@

\begin{definition}
  \label{def_spectrahedra}
  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \mathcal{M}_n(K)$ be an affine space, for some
  $A_0,A_1,\ldots,A_n \in \mathcal{M}_n(K)$.
  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ or equivalently,
  its canonical preimage in $K^n$:
  $$
  S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\},
  $$
  is called a \emph{spectrahedron}.
\end{definition}

\begin{remark}
  The class of spectrahedra is closed under intersection. Indeed, for affine spaces $\mathcal{L}_1,\mathcal{L}_2$
  one has $(\mathcal{L}_1 \cap \mathcal{M}_n^+(K)) \cap (\mathcal{L}_2 \cap \mathcal{M}_n^+(K)) =
  (\mathcal{L}_1\cap\mathcal{L}_2) \cap \mathcal{M}_n^+(K)$. Now
  assuming $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = B_0+\span{B_1,\ldots,B_n}$,
  then 
\end{remark}

%\begin{remark}
%	As in the real case, the spectrahedron associated with the affine plan $\mathcal{L}$ will often be identified with its preimage in $K^s$ (i.e. the set of vectors $x \in K ^s$ so that the linear matrix $A(x) = A_0 + x_1A_1 + \ldots + x_sA_s$ is positive semidefinite with $A_0,A_1,\ldots,A_s$ spanning $\mathcal{L}$). 
%\end{remark}
\begin{proposition}
  A polyhedron is a spectrahedron.
\end{proposition}
\begin{proof}
  Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
  be the polyhedron given in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
  and $L = \{x \in K^n : \val(m_j) = 0, j=1,\ldots,e\}$.
  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d$, so that $Q$ is the (preimage of the)
  spectrahedron defined by $A(x) \succeq 0$.
  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$.

>>>>

We recall that that the smallest affine space of $K^n$ containing a set $S \subset K^n$ is called its
\emph{affine hull} and denoted $\aff{S}$.
The assumption on forms $\ell_i$ in \Cref{def_polyhedra} implies that the constraint
$\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ defines exactly the affine hull of $P$, in other words
$\aff{P} = \{x \in K^n : m_j(x) = 0,
j=1,\ldots,e\}$ (\simone{il nous faudrait une preuve}).
The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$,
$\aff{P}=K^n$ and $P$ has dimension $n$).
The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d)
< +\infty\}$ (\simone{pas clair si besoin de dimension et relint}).
Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.

@@

\begin{definition}
  \label{def_spectrahedra}
  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \mathcal{M}_n(K)$ be an affine space, for some
  $A_0,A_1,\ldots,A_n \in \mathcal{M}_n(K)$.
  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ is called a \emph{spectrahedron}. Its 
  its canonical preimage $S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}$
  is also called spectrahedron.
\end{definition}

\begin{remark}
  The class of spectrahedra is closed under intersection. Indeed, for affine spaces $\mathcal{L}_1,\mathcal{L}_2$
  one has $(\mathcal{L}_1 \cap \mathcal{M}_n^+(K)) \cap (\mathcal{L}_2 \cap \mathcal{M}_n^+(K)) =
  (\mathcal{L}_1\cap\mathcal{L}_2) \cap \mathcal{M}_n^+(K)$. Now
  assuming $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = B_0+\span{B_1,\ldots,B_n}$,
  then $S_A \cap S_B = S_{A \oplus B}$ (indeed both $A \succeq 0$ and $B \succeq 0$ if and only if
  $A \oplus B \succeq 0$).
\end{remark}

%\begin{remark}
%	As in the real case, the spectrahedron associated with the affine plan $\mathcal{L}$ will often be identified with its preimage in $K^s$ (i.e. the set of vectors $x \in K ^s$ so that the linear matrix $A(x) = A_0 + x_1A_1 + \ldots + x_sA_s$ is positive semidefinite with $A_0,A_1,\ldots,A_s$ spanning $\mathcal{L}$). 
%\end{remark}
\begin{proposition}
  A polyhedron is a spectrahedron.
\end{proposition}
\begin{proof}
  Let $\ell_i,m_j \in K[x]_1$, for $i=1,\ldots,d$ and $j=1,\ldots,e$, and let $P = Q \cap L \subset K^n$
  be a polyhedron as in \Cref{def_polyhedra}, for $Q = \{x \in K^n : \val(\ell_i) \geq 0, i=1,\ldots,d\}$
  and $L = \{x \in K^n : \val(m_j) = 0, j=1,\ldots,e\}$.
  First, denote by $A(x) = \ell_1 \oplus \cdots \oplus \ell_d$, so that $Q$ is the (preimage of the)
  spectrahedron defined by $A(x) \succeq 0$.
  Next, remark that $L \subset K^n$ is the affine space defined by equations $m_1=\ldots=m_e=0$.
